---
title: "rgates vinette"
author: "Muhammad Ezzat"
date: "3/12/2020"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r,include=FALSE}
check_bool <- function(x){
  if(class(x)!='logical'){
    stop("Input must be a logical variable")
  }

}
check_length <- function(x,y){
  if(length(x)!=length(y))
    stop("Both inputs must be of same length")
}
truth_table <- function(){
  x <- c(FALSE,FALSE,TRUE,TRUE)
  y <- c(FALSE,TRUE,FALSE,TRUE)
  foo <- data.frame(x,y)
  return(foo)
}
not <- function(x){
  check_bool(x)
  return(!x)
}
and <- function(x,y){
  check_bool(x)
  check_bool(y)
  check_length(x,y)
  return(x&y)
}
or <- function(x,y){
  check_bool(x)
  check_bool(y)
  check_length(x,y)
  return(x|y)
}
nand <- function(x,y){
  check_bool(x)
  check_bool(y)
  check_length(x,y)
  return(!and(x,y))
}
nor <- function(x,y){
  check_bool(x)
  check_bool(y)
  check_length(x,y)
  return(!or(x,y))
}
xor <- function(x,y){
  check_bool(x)
  check_bool(y)
  check_length(x,y)
  return(x!=y)
}
xnor <- function(x,y){
  check_bool(x)
  check_bool(y)
  check_length(x,y)
  return(x==y)
}
implies <- function(x,y){
  check_bool(x)
  check_bool(y)
  check_length(x,y)
  z <-rep(TRUE,length(x))
  for(i in c(1:length(z)))
    if(x[i] == TRUE & y[i] == FALSE)
      z[i] <- FALSE
  return(z)
}
null <- function(x){
  if(class(x)!='numeric')
    stop('Input must be a number')
  x <- as.integer(x)
  return(rep(FALSE,x))
}
on <- function(x){
  if(class(x)!='numeric')
    stop('Input must be a number')
  x <- as.integer(x)
  return(rep(TRUE,x))
}
inhibit <- function(x,y){
  check_bool(x)
  check_bool(y)
  check_length(x,y)
  return(x&(!y))
}
transefer <- function(x){
  check_bool(x)
  return(x)
}


```

# Introduction 
Digital Logic designers build complex electronic components that use both electrical and computational characteristics. These characteristics may involve power, current, logical function, protocol and user input. Digital Logic Design is used to develop hardware, such as circuit boards and microchip processors.

Logic gates are the basic building blocks of any digital system. It is an electronic circuit having one or more than one input and only one output. The relationship between the input and the output is based on a certain logic. Based on this, logic gates are named as AND gate, OR gate, NOT gate etc.

# The rgates package
The rgates package aim to simulate logic gates for 2 variables. In fact the number of possible boolean fucntions that can be implemented on logic gates is 2 raised to the power of double the number of values. In our case its 2^(2*2) which evaluates to 16. On first thought this needs 16 fucntions to represent, but actually somw fucntions are input order sensitive so a change in input order is considered a new fucntion. Thus the number of functions is reduced to 12 instead of 16. However 2 helper functions were created in addition to 1 complementary function so we have 15 functions in total.

# Tutorial
Let's walk through the package and implement the rgates package fucntions. First we will create two logical vectors that form all of the possible logical combinations through the truth_table() function.
```{r,include=TRUE}
df <- truth_table()
print(df)
```
As you saw it creates a data frame of two vectors representing the two variables that include all the possible logical combinations to get. Now let's explore our gates.

## Not gate
Also known as the inverter it returns false from a true input & vise versa.
```{r,include=TRUE}
print(df$x)
print(not(df$x))
```
## And gate
The equivalence of the '&' sign in R & most of the programming languages, returns true only if both inputs are so.
```{r,include=TRUE}
print(df$x)
print(df$y)
print(and(df$x,df$y))
```
## Or gate
The equivalence of the '|' sign in R & most of the programming languages, returns false only if both inputs are so.
```{r,include=TRUE}
print(df$x)
print(df$y)
print(or(df$x,df$y))
```
## Nand gate
Simply the inverse of the and gate, you can write x nand y as !(x&y). We will confirm this right at the moment using rgates package.
```{r,include=TRUE}
print(df$x)
print(df$y)
print(nand(df$x,df$y))
print(not(and(df$x,df$y)))
```
## Nor gate
Similarly, the nor gate is the inverse of the or gate.
```{r,include=TRUE}
print(df$x)
print(df$y)
print(nor(df$x,df$y))
print(not(or(df$x,df$y)))
```
## Xor gate
XOR gate (sometimes EOR, or EXOR and pronounced as Exclusive OR) is a digital logic gate that gives a true (1 or HIGH) output when the number of true inputs is odd. An XOR gate implements an exclusive or; that is, a true output results if one, and only one, of the inputs to the gate is true.
```{r,include=TRUE}
print(df$x)
print(df$y)
print(xor(df$x,df$y))
```
## Xnor gate
Mathematically it represents the equivellance state, returns true if both inputs are of the same value.
```{r,include=TRUE}
print(df$x)
print(df$y)
print(xnor(df$x,df$y))
```
## Implification gate
An implication is something that is suggested, or happens, indirectly. When you left the gate open and the dog escaped, you were guilty by implication. Usually, when used in the plural, implications are effects or consequences that may happen in the future. However in logic  An implication is the compound statement of the form “if p, then q.” It is denoted p⇒q, which is read as “p implies q.” It is false only when p is true and q is false, and is true in all other situations.
```{r,include=TRUE}
print(df$x)
print(df$y)
print(implies(df$x,df$y))
```
## Inhibition gate
Instead of a long explaination we can just coin the term "X but not Y". So it only returns true if x is but y isn't.
```{r,include=TRUE}
print(df$x)
print(df$y)
print(inhibit(df$x,df$y))
```
## BinaryConstant gate
They produce either true or false for whatever the length you need 
```{r,include=TRUE}
print(on(3))
print(null(3))
```
## Transefer gate
Another very simple gate, baiscally it returns it's input, it's usage in real life is a sort of amplifier when the curcuit power loss effect appears on your signals. It was provided by the rgates package for convenience.
```{r,include=TRUE}
print(df$x)
print(transefer(df$x))
```

## Chaining 
You probably noticed that you can chain many gates together, here is an example
```{r,include=TRUE}
print(implies(and(df$y,xor(df$x,on(4))),null(4)))
```
### Warnings
All of these functions throw errors for non logical type input and for inputs not equal in length. This package is compeletly safe to use as it passed the TRAVIS CL test & RStudio test. The package is under the CC0 license which means anybody can use it for free. If you have any issue contact the maintainer : muhammadezzat316@gmail.com.
Github repo : https://github.com/MuhammadEzzatHBK/rgates2 . 




